\documentclass{article}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{\textbf{Business Requirement Document (BRD)}
\vspace{10pt}
\\\large \textbf{Project Title: SpendSmart}}
\author{Prepared by: Aashin K S \& Avula Venumadhav}
\date{}

\begin{document}

\maketitle

\section{Project Overview}
Managing personal finances can be difficult, especially for individuals who lack financial literacy or have impulsive spending habits.
Traditional budgeting tools often require manual entry and offer limited guidance, leaving users overwhelmed.

SpendSmart aims to automate personal finance management by integrating with global financial APIs to fetch real-time bank transaction data, help users track expenses, manage budgets, receive financial advice via an AI-powered chatbot, and stay informed with personalized alerts—all from a single intuitive platform.

\section{Business Goals}
\begin{itemize}
    \item Enable users to link their bank accounts securely and automatically import transactions.
    \item Automate expense tracking and categorize spending intelligently.
    \item Provide personalized financial insights and budget alerts.
    \item Help users set, monitor, and achieve their savings goals.
    \item Ensure a scalable, secure, and user-friendly platform with microservices architecture.
\end{itemize}

\section{User Stories}
\begin{itemize}
    \item As a user, I want to securely link my bank account to automatically fetch my transactions.
    \item As a user, I want my expenses to be automatically categorized to understand my spending.
    \item As a user, I want to receive smart alerts when I'm close to exceeding my budget.
    \item As a user, I want to create savings goals and track progress.
    \item As a user, I want to view monthly and yearly spending summaries and financial health.
    \item As a user, I want to interact with a chatbot for personalized financial advice.
    \item As an admin, I want to manage user accounts, monitor platform usage, and ensure security.
\end{itemize}

\section{Solutions Provided by SpendSmart}
\begin{itemize}
    \item Bank Integration: Securely link and fetch bank transactions via APIs like Plaid.
    \item Automatic Expense Categorization: Classify transactions by merchant, category, and pattern.
    \item Smart Budget Planner: Define monthly/annual budgets, with real-time monitoring.
    \item Goal Tracker: Set, edit, and monitor savings goals and track achievements.
    \item AI-Driven Chatbot: Financial advice chatbot powered by Ollama LLM models.
    \item Email Notifications: Important updates and alerts via Nodemailer.
    \item Interactive Dashboard: Visual charts and summaries for income, expenses, goals, and trends.
\end{itemize}

\section{Tech Stack}
\begin{itemize}
    \item Backend: Node.js, Express.js
    \item Frontend: Angular
    \item Database: MongoDB (via Mongoose)
    \item API Gateway: Express Gateway (for routing and API management)
    \item Third-Party APIs:
    \begin{itemize}
        \item Plaid API (Bank linking and transactions)
        \item Ollama LLM (Financial advice chatbot)
    \end{itemize}
    \item Email Service:
    \begin{itemize}
        \item Nodemailer (for sending email notifications)
    \end{itemize}
\end{itemize}

\section{Key Milestones}
\begin{enumerate}
    \item Backend Setup: Node.js + Express.js services for Authentication, Bank Account Linking, Transaction Fetching and Categorization, Budget and Goal Management, Notification Services, AI Chatbot Microservice.
    \item Frontend Setup: Angular development, UI component creation, User-friendly routing.
    \item API Gateway Setup: Setup Express Gateway, Configure services, routes, and policies for security and load management.
    \item Third-Party API Integration: Plaid, Ollama, Nodemailer integration.
    \item UI/UX Designing: Responsive designs for Dashboard, Budget Tracker, Goal Management, Transaction Insights, and Chatbot Interface.
    \item Frontend-Backend Integration: Connect Angular frontend to Node.js backend via Express Gateway.
    \item Testing \& Deployment: Perform full-stack testing, optimize performance, and deploy to cloud (e.g., AWS).
\end{enumerate}

\section{Deliverables}
\begin{itemize}
    \item Full-stack responsive web application (MEAN stack)
    \item Secure bank linking and transaction integration
    \item Categorized transaction dashboard
    \item Budget management and goal tracking modules
    \item AI-powered financial chatbot
    \item REST APIs with full documentation
    \item Admin control panel (for user and system management)
    \item Deployed application with user instructions
    \item Data privacy and security compliance documentation
\end{itemize}

\end{document}
